\section{Results}\label{sec:results}

\subsection{Predicted Harris Effects Across Models}

Table~\ref{tab:harris_effects} shows the predicted effects under a Harris administration across three main outcomes: air quality (PM2.5), GDP per capita, and poverty rate. All models predict improvements under a Harris administration, with reductions in PM2.5 and poverty rates and an increase in GDP per capita.

While the general direction of these effects is consistent, the magnitude varies by model. For example, the Grok model predicts the largest impact across all outcomes, with a PM2.5 reduction of 1.51 $\mu g/m^3$ (SE: 0.02, p < 0.001) and a poverty rate reduction of 3.42 percentage points (SE: 0.07, p < 0.001). GPT-4o-mini, on the other hand, consistently shows more modest effects, predicting a PM2.5 reduction of just 0.15 $\mu g/m^3$ (SE: 0.02, p < 0.001) and a poverty rate reduction of 0.68 percentage points (SE: 0.07, p < 0.001).

\begin{table}[htbp]
    \centering
    \caption{Predicted Harris Effects by Model}
    \begin{tabular}{lccc}
    \hline
    Outcome & GPT-4o & GPT-4o-mini & Grok \\
    \hline
    Mean PM2.5 ($\mu g/m^3$) & -1.26*** (0.02) & -0.15*** (0.02) & -1.51*** (0.02) \\
    GDP per Capita (\$) & 387.61*** (103.05) & 264.25*** (103.16) & 802.47*** (104.48) \\
    Supplemental Poverty Measure (pp) & -1.76*** (0.07) & -0.68*** (0.07) & -3.42*** (0.07) \\
    \hline
    \multicolumn{4}{p{0.8\textwidth}}{\small Note: Standard errors in parentheses. Significance levels: * p<0.05, ** p<0.01, *** p<0.001} \\
    \end{tabular}
    \label{tab:harris_effects}
\end{table}

\subsection{Significance of Model Differences}

\begingroup
\renewcommand{\_}{\string_}
\input{../llm_forecasts/outputs/model_comparison_table_20241104_043856}
\endgroup

The results indicate that GPT-4o-mini generally produces smaller effect sizes compared to GPT-4o, with significant differences observed in the reduction of PM2.5 (1.11 $\mu g/m^3$, p < 0.001) and poverty rate (1.08 percentage points, p < 0.001). The Grok model, conversely, predicts larger effects in all areas, with a notable increase in GDP effect of 414.86 (p < 0.01). These discrepancies suggest that GPT-4o-mini and Grok diverge in their approach to effect prediction.

For full implementation, see the repository at \url{https://github.com/MaxGhenis/llm-presidential-outcome-forecasts}.